Enhanced Material Point Method to face dynamic problems:\thanks{Funding: This study was funded by Agustín de Betancourt Foundation (grant number 262390106114).}

### 2020-03-23 main.tex
Mejora figuras
Cambios text 23-03-2020

@@

\subsection{Galerkin procedure}
\label{sec:Galerkin-procedure}
In order to arrive to a finite set of equations, in contrast with the
FEM, in the MPM a double discretization procedure is performed as we will
describe here below. First, the continuum domain
$\Omega$ is discretized with a finite sum of material points (in the
following particles), each one
represent a part of the discretized domain $\varOmega_p \subset
\varOmega$ with $p = 1,2\ldots ,N_p$ where $N_p$ is the number of
particles. The material point $\vec{x}_p$ is defined at the centroid
of each $\Omega_p$, figure \ref{fig:MPM-discretization}.
\begin{figure}\sidecaption
  \centering
  \resizebox{0.9\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
  }
  \caption{MPM discretization.}
  \label{fig:MPM-discretization}
\end{figure}

@@

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_05}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Dyka-PCE-FE}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity_LME_gamma_comparative}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Dyka-LME-gamma}
\end{figure}

>>>>

\usetikzlibrary{%
    decorations.pathreplacing,%
    decorations.pathmorphing%
}

@@

\subsection{Galerkin procedure}
\label{sec:Galerkin-procedure}
In order to arrive to a finite set of equations, in contrast with the
FEM, in the MPM a double discretization procedure is performed as we will
describe here below. First, the continuum domain
$\Omega$ is discretized with a finite sum of material points (in the
following particles), each one
represent a part of the discretized domain $\varOmega_p \subset
\varOmega$ with $p = 1,2\ldots ,N_p$ where $N_p$ is the number of
particles. The material point $\vec{x}_p$ is defined at the centroid
of each $\Omega_p$, figure \ref{fig:MPM-discretization}.

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \input{Figures/Discretization_MPM.tex}}
  \caption{MPM discretization.}
  \label{fig:MPM-discretization}
\end{figure}

% \begin{figure}\sidecaption
%   \centering
%   \resizebox{0.9\hsize}{!}{
%     \includegraphics[width=\textwidth]{./Figures/Discretization_MPM}
%   }
%   \caption{MPM discretization.}
%   \label{fig:MPM-discretization}
% \end{figure}

@@

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_01}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Dyka-PCE-FE}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Dyka-LME-gamma}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity_uGIMP_vs_LME_Dyka}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Dyka-uGIMP-LME}
\end{figure}
